---
title: "echoconda: Getting Started"
author: "Brian M. Schilder"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: show
vignette: >
    %\VignetteIndexEntry{echoconda}
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r, eval = TRUE}
library(echoconda)
```

# Introduction

`echoconda` provides robust utilities to find, build, use, and export
conda environments from within R. It wraps `reticulate` and `basilisk`
to give a consistent, cross-platform interface for managing Python
dependencies needed by the echoverse tool suite.

# Conda

## Install conda

If conda is not yet available on your system, `echoconda` can install
Miniconda for you:
```{r}
echoconda::install_conda()
```

## Build an environment from YAML

Will build the "echoR_mini" conda environment by default.

```{r}
conda_env <- echoconda::yaml_to_env("echoR_mini")
```

## Export an environment to YAML

```{r}
yaml_path <- echoconda::env_to_yaml(conda_env = "echoR_mini")
```

## Activate a conda environment

```{r}
echoconda::activate_env(conda_env = "echoR_mini")
```

## List available environments

```{r}
envs <- echoconda::list_envs()
print(envs)
```

## Find packages in an environment

```{r}
pkgs <- echoconda::find_packages(
  packages = c("python", "tabix", "axel"),
  conda_env = "echoR_mini"
)
knitr::kable(pkgs)
```

## Find the Python path

```{r}
python <- echoconda::find_python_path(conda_env = "echoR_mini")
print(python)
```

# Import CLI tools

In addition, `echoconda` can automatically convert command-line
interface (CLI) tools into R functions.

## Example: tabix

Here we use a conda-installed version of `tabix` as an example.

```{r}
#### Import tool ####
tabix <- echoconda::import_cli(
  path = "tabix",
  conda_env = "echoR_mini"
)

#### Use function to query a file ####
target_path <- system.file("extdata", "BST1.1KGphase3.vcf.bgz",
                           package = "echodata")
query <- "4:5000-100000000"

res <- tabix(D = TRUE,
             h = TRUE,
             ... = paste(target_path, query))
dat <- data.table::fread(text = res, skip = "#CHROM")
```

# Session Info

<details>

```{r Session Info, eval = TRUE}
utils::sessionInfo()
```

</details>

<br>
