---
title: "``r read.dcf('../DESCRIPTION', fields = 'Package')[1]``: Getting Started" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>" 
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{echodata} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup}
library(echoconda) 
```


# conda

`echoconda`'s primary purpose is to robustly build, use and export 
conda environments from within R.

## Build env from yaml

Will build the "echoR_mini" conda environment by default.

```{r}
conda_env <- echoconda::yaml_to_env("echoR_mini")
```

## Export 

```{r}
yaml_path <- echoconda::env_to_yaml(conda_env = "echoR_mini")
```


## Activate conda env

```{r}
echoconda::activate_env(conda_env = "echoR_mini")
```

## Find package path 

```{r}
pkgs <- echoconda::find_packages(packages = c("python","tabix","axel"),
                                 conda_env = "echoR_mini")
knitr::kable(pkgs)
```

## Find python path

```{r}
python <- echoconda::find_python_path(conda_env = "echoR_mini")
print(python)
```


# import CLI

In addition, `echoconda` has some functionality for automatically converting 
command line interface (CLI) tools into R functions. 

## tabix

Here we will use a conda-installed version of tabix as an example.

```{r}
#### Import tool ####
tabix <- echoconda::import_cli(path = "tabix",
                               conda_env = "echoR_mini")

#### Use function to query file ####
target_path <- system.file("extdata", "BST1.1KGphase3.vcf.bgz",
                           package = "echodata")
query <- "4:5000-100000000"

res <- tabix(D = TRUE, 
             h = TRUE,
             ... = paste(target_path, query))
dat <- data.table::fread(text = res, skip = "#CHROM")

```


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

<br>

